Vertical shear instability in astrophysical disks: vertically global linear calculations with thermal relaxation and applications to the Solar Nebula

### 2015-03-16 numerical.tex
revised

In Fig. \ref{compare_modes_cool_kx30} we plot eigenvalues for unstable
modes with $\khat=30$. For clarity, we only plot analytic results 
for the fundamental mode ($M=0$) and $M=1,\,2$, and omit the
squares. The fundamental mode is again insensitive boundary
conditions compared to higher order modes, and are in close agreement
with analytic results. As before we observe more effective
stabilization for higher order modes, including the absence of surface
modes (which only occur for $\zmax\geq 5H$) as $\beta$ is increased.  
For $\zmax=3H$, the fundamental mode becomes dominant for $\beta\geq
0.03$. For $\zmax=5H$ and $\zmax=7H$, we
find modes slightly more unstable than the fundamental
mode even when $\beta=0.1$ (the leftmost eigenvalues in the lower two
panels), but these are likely associated  with the boundary
condition as they are absent for $\zmax=3H$. These observations
suggest the fundamental mode to be more robust in realistic disks.

>>>>

In Fig. \ref{compare_modes_cool_kx30} we plot eigenvalues for unstable
modes with $\khat=30$. For clarity, we only plot analytic results 
for the fundamental mode ($M=0$) and $M=1,\,2$, and omit the
squares. The fundamental mode is again insensitive boundary
conditions compared to higher order modes, and are in close agreement
with analytic results. As before we observe more effective
stabilization for higher order modes, including the absence of surface
modes (which only occur for $\zmax\geq 5H$) as $\beta$ is increased.  
For $\zmax=3H$, the fundamental mode becomes dominant for $\beta\geq
0.03$. For $\zmax=5H$ and $\zmax=7H$, we
find modes slightly more unstable than the fundamental
mode even when $\beta=0.1$ (the leftmost eigenvalues in the lower two
panels), but these are clearly associated with boundary
conditions as they are absent for $\zmax=3H$. These observations
suggest the fundamental mode to be more robust in realistic disks.
